Foraging: The Triumphant Return

### 2022-05-09 manuscript.tex
Updates from Overleaf

\begin{equation}
    w_i = g\left(b_at_i + b_sm(t_i, t_{i-1})\right) \times \rho_d(i, i-1) \rho_{\theta}(i, i-1)
\end{equation}

@@

\begin{equation}
    \rho_d = e^{-\sigma_dd(i,j)}
\end{equation}
\begin{equation}
    \rho_{\theta} = e^{-\sigma_d\theta(i,j)}
\end{equation}

$d(i,j)$ is simply the Euclidean distance between items $i$ and $j$, while $\theta$ is defined as:
\begin{equation}
    \theta(i,j) = \frac{f(\text{atan2}(i, j) - \text{atan2}(i-1, i))}{\pi}
\end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

\subsection{Initial target selection}

@@

\subsection{Improvement: Adaptive distance? Absolute direction?}

@@

This is the example 2 of equation:
\begin{adjustwidth}{-\extralength}{0cm}
\begin{equation}
a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
\end{equation}
\end{adjustwidth}

>>>>

\begin{linenomath}
\begin{equation}
    w_i = g\left(b_at_i + b_sm(t_i, t_{i-1})\right) \times \rho_d(i, i-1) \rho_{\theta}(i, i-1)
\end{equation}
\end{linenomath}

@@

\begin{linenomath}
\begin{equation}
    \rho_d = e^{-\sigma_dd(i,j)}
\end{equation}
\end{linenomath}

\begin{linenomath}
\begin{equation}
    \rho_{\theta} = e^{-\sigma_d\theta(i,j)}
\end{equation}
\end{linenomath}

$d(i,j)$ is simply the Euclidean distance between items $i$ and $j$, while $\theta$ is defined as:

\begin{linenomath}
\begin{equation}
    \theta(i,j) = \frac{f(\text{atan2}(i, j) - \text{atan2}(i-1, i))}{\pi}
\end{equation}
\end{linenomath}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results: Evaluating the Model}

@@

\section{Results: Improving the model}

One weakness of the foraging model by \cite{clarke2022foraging} is that it makes little attempt to the predict which item will be selected first. IN this section we aim to improve this by modelling participant bias/preference in their choice of initial target selection. Following \cite{clarke_tatler2014, clarke2017} we fit truncated Gaussian distributions to the $(x,y)$ coordinates of the initial target selections

\section{Foraging in 3D virtual environments}

Can we model the data from \cite{prpic2019}?

\subsection{Fitting the Model}

\begin{figure}[H]
\centering
\includegraphics[width=12 cm]{Figures/prpic_model_params.pdf}
\caption{(\textit{top}) Figure caption needed}
\label{fig:qjep_paths}
\end{figure}

@@
